\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Marlon Mejia}}\\
	New Jersey, United States $\cdot$ marlon.junior.mejia@gmail.com $\cdot$ 631-480-7675 $\cdot$ https://linkedin.com/in/marlon-mejia\\
\end{center}

%==== Experience ====%
\header{Experience}
\vspace{1mm}

\textbf{Bloomberg LP} \hfill New Jersey\\
\textit{Datacenter Operations Specialist} \hfill Nov 2020 - July 2024\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Address Layer 1 \& 2 connectivity issues Led a project to automate case opening and log gathering across multiple systems and network devices, reducing operation time by over 98\%, from more than 20 minutes to just 30 seconds per task.across 1000+ servers, switches, routers, and firewalls.
	\item Address issues across operating systems, including Windows and Linux (Red Hat, Debian) to ensure reliable functionality.
	\item Address Layer 1 \& 2 connectivity issues across 1000+ servers, switches, routers, and firewalls.
	\item Reduced operation time from over *20 minutes* to just 30 seconds per task, saving approximately 1690 hours annually.
	\item Develope over 50 Dockerfiles to containerize and facilitate consistent deployment and testing of Python and Bash
	\item Utilize Jira to plan, track, and manage incidents, ensuring efficient resolution.
	\item Contribute to the modernization of legacy scripts and overhaul of outdated documentation.
	\item Oversaw operating systems and network hardware across datacenters, tracking disruptions, resource utilization, and power consumption
	\item Execute regular audits of data center operations, identifying improvement opportunities and implementing strategies to enhance performance and reduce costs.
	\item Collaborated across multiple technical teams to deliver Agile-based projects, ensuring seamless communication and coordination.
	\item Perform routine maintenance, hardware upgrades, firmware updates, and patch management, to ensure peak system performance.
	\item Rack and Stack: Installed and configured servers and network equipment.
	\item Decommissioning: Managed server and cable removal, data sanitization, and disposal.
	\item Modernize legacy documentation to align with current industry standards while enhancing operational efficiency through advance Bash and Python automation tools.
\end{itemize}
\textbf{NYI - New York Internet} \hfill New York, United States\\
\textit{Datacenter Technician} \hfill Jul 2020 - Nov 2020\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Provided remote technical support, including device configuration, troubleshooting, and optimization.
	\item Monitored over 1000 devices using LogicMonitor, ConnectWise, and Meraki resolved outages and network issues.
	\item Automated Google Drive tasks with Python scripts using Drive API.
	\item Installed and organized hardware, performed cabling and tested with Fluke equipment.
	\item Communicated with clients about services and provided performance tips.
	\item Documented server setups and task methodologies for efficient handovers.
\end{itemize}

\header{Certifications}
\textbf{Red Hat Certified System Administrator} \hfill Red Hat\\
Able to perform the core system administration skills required in Red Hat Enterprise Linux environments \hfill Apr 2022\\
\vspace*{2mm}
\textbf{AWS SAA-C03} \hfill Amazon\\
Validates a candidateability to design solutions based on the AWS Well-Architected Framework \hfill March 2023\\
\vspace*{2mm}
\textbf{Security+} \hfill Comptia\\
Global certification that validates the baseline skills necessary to perform core security functions \hfill November 2020\\
\vspace*{2mm}
\textbf{A+} \hfill Comptia\\
Basic Technologies and skills IT pros need to support a hybrid workforce. \hfill May 2020\\
\vspace*{2mm}
\textbf{API Security Architect} \hfill apiacademy\\
Identify security risks of API\textquotesingle{}s and typical areas of API vulnerabilities \hfill Jan 20 2024\\
\vspace*{2mm}

\header{Skills}
\begin{tabular}{ l l }
	Programming:            & Python, Bash, Powershell                           \\
	Tools:                  & Docker, Active Directory, GitHub, Gitlab, Crowdsec \\
	Infrastructure-as-Code: & Terraform, Ansible                                 \\
	CI/CD:                  & Jenkins, Github Actions, AWS CodePipeline          \\
	Operating System:       & Linux (RedHat, Debian), Windows, Unix              \\
	Programming:            & Bash, Python, Powershell                           \\
	Monitoring:             & Grafana, Splunk, Humio, Prometheus, Influxdb       \\
	Databases:              & MariaDB, MySQL, NoSQL                              \\
	Cloud:                  & AWS, ECS, EC2, VPC, IAM                            \\
\end{tabular}
\vspace{2mm}

\header{Projects}
{\textbf{CI/CD Project for AWS and GitHub Pages}} {\sl AWS, Github Actions, Python, Hugo, AWS CodePipeline} \hfill marlonjmejia.github.io\\
Developed a robust CI/CD pipeline to automate the deployment of a static website hosted on AWS.\\
\vspace*{2mm}
{\textbf{Cloud Proxy Server}} {\sl Wireguard, Ansible, Terraform, Github, Opnsense, Proxmox} \hfill wiki.402error.duckdns.org\\
Designed and automated the deployment of secure, scalable cloud infrastructure on Oracle Cloud to expose local resources.\\
\vspace*{2mm}
{\textbf{Proxmox Provisioning}} {\sl Ansible, Terraform, Proxmox} \\
Streamlined the provisioning and configuration of LXC containers and VM instances on Proxmox\\
\vspace*{2mm}



\ 
\end{document}